---
title: "Bayesian_analysis"
author: "Laura Bock Paulsen and Emma Risgaard Olsen"
date: "6/7/2022"
output: html_document
---

```{r}
library(rethinking)
pacman::p_load(tidyverse, cowplot, ggplot2)
```


## Preparing the data
To begin with the data is loaded, and a column is created with the intervention
```{r}
blinding1 <- read_csv('data1/data_blinding.csv')
blinding2 <- read_csv('data2/data_blinding.csv')
blinding3 <- read_csv('data3/data_blinding.csv')
blinding4 <- read_csv('data4/data_blinding.csv')

blinding <- rbind(blinding1, blinding2, blinding3, blinding4)
blinding$intervention <- 4

shortlist1 <- read_csv('data1/data_shortlist.csv')
shortlist2 <- read_csv('data2/data_shortlist.csv')
shortlist3 <- read_csv('data3/data_shortlist.csv')
shortlist4 <- read_csv('data4/data_shortlist.csv')

shortlist <- rbind(shortlist1, shortlist2, shortlist3, shortlist4)
shortlist$intervention <- 3

parental1 <- read_csv('data1/data_shared_parental.csv')
parental2 <- read_csv('data2/data_shared_parental.csv')
parental3 <- read_csv('data3/data_shared_parental.csv')
parental4 <- read_csv('data4/data_shared_parental.csv')

parental <- rbind(parental1, parental2, parental3, parental4)
parental$intervention <- 2

nointervention1 <- read_csv('data1/data_no_intervention.csv')
nointervention2 <- read_csv('data2/data_no_intervention.csv')
nointervention3 <- read_csv('data3/data_no_intervention.csv')
nointervention4 <- read_csv('data4/data_no_intervention.csv')

nointervention <- rbind(nointervention1, nointervention2, nointervention3, nointervention4)
nointervention$intervention <- 1
```

Then the data frames are merged and filtered as to only contain the last tick
```{r}
df <- rbind(blinding, shortlist, parental, nointervention) %>% filter(tick == 59)
```


Then the data list is prepared for the model
```{r}
dat <- list(
  S = as.integer(ifelse(df$gender == 'male', 0 , 1)),
  In = as.integer(df$intervention),
  L = as.integer(as.factor(df$position))
)
```

```{r}
unique(dat$In)
unique(dat$L)
unique(dat$S)
```

```{r}
m <- ulam(
 alist(S ~ dbern(p),
    logit(p) <- I[In,L],
    matrix[In, L]:I ~ normal(0, 0.5)
    ) , data=dat, chains=4, cores = 4, refresh=0)
```

```{r}
precis_plot(precis(m, depth = 3))
```
### Prior predictive checks
```{r}
prior <- extract.prior(m)
```

```{r}
predictions <- link(m, post = prior, data = dat)
priormeans <- rowMeans(predictions)
dens(priormeans, main="Means of Prior Predictions Across All Agents")
```

### Posterior predictive checks
```{r}
post_int <- extract.samples(m)
predictions <- link(m, post = post_int, data = dat)
postmeans <- rowMeans(predictions)
dens(postmeans, main="Means of Posterior Predictions Across All Agents")
```

```{r}
predicted_gender <- sim(m, dat)
mean_predicted <- round(colMeans(predicted_gender), 0)
table(dat$S, mean_predicted)
```


### Intervention contrast
```{r}
plot_contrasts <- function(level, xlim, ylim){
  
  title <-paste('Level', level)
  
  PrS <- inv_logit(post_int$I)
  diff_prob <- as.tibble(sapply(2:4, function(i) PrS[, i, level] - PrS[, 1, level]))
  colnames(diff_prob) <- c("Parental Leave", "Shortlist", "Blinding")
  data_long <- gather(diff_prob, Intervention, measurement, 'Parental Leave':'Blinding')
  
  p <- ggplot(data_long, aes(x = measurement, color = Intervention)) + 
    geom_density() +
    scale_colour_brewer(palette="Paired") +
    xlab('Contrast against baseline (Probabilities)')+
    ylab('Density')+
    ggtitle(title) +
    theme_classic()+
    theme(legend.position = c(0.8, 0.8))
  p
  
    
  
  return(p)
}
```




```{r}
p6 <- plot_contrasts(6, xlim = c(-0.05, 0.15), ylim = c(0, 40))
p5 <- plot_contrasts(5, xlim = c(-0.1, 0.05), ylim = c(0, 40))
p4 <- plot_contrasts(4, xlim = c(-0.1, 0.1), ylim = c(0, 20))
p3 <- plot_contrasts(3, xlim = c(-0.2, 0.2), ylim = c(0, 15))
p2 <- plot_contrasts(2, xlim = c(-0.4, 0.4), ylim = c(0, 10))
p1 <- plot_contrasts(1, xlim = c(-0.5,0.5), ylim = c(0, 5))

p6
p5
p4
p3
p2
p1
```


```{r}
plot_grid(p1, p2, p3, p4, p5, p6)
```


#### Relative effect sizes

```{r}
mean(exp(post_int$I[,2,6] - post_int$I[,1,6])) # Intervention, Level
mean(exp(post_int$I[,3,6] - post_int$I[,1,6])) # Intervention, Level
mean(exp(post_int$I[,4,6] - post_int$I[,1,6])) # Intervention, Level
```
What does this mean? When switching from baseline (intervention 1) to each of the other interventions, the odds of agents being female is multiplied by ____


```{r}
mean(exp(post_int$I[,2,5] - post_int$I[,1,5])) # Intervention, Level
mean(exp(post_int$I[,3,5] - post_int$I[,1,5])) # Intervention, Level
mean(exp(post_int$I[,4,5] - post_int$I[,1,5])) # Intervention, Level
```

```{r}
mean(exp(post_int$I[,2,4] - post_int$I[,1,4])) # Intervention, Level
mean(exp(post_int$I[,3,4] - post_int$I[,1,4])) # Intervention, Level
mean(exp(post_int$I[,4,4] - post_int$I[,1,4])) # Intervention, Level
```

```{r}
mean(exp(post_int$I[,2,3] - post_int$I[,1,3])) # Intervention, Level
mean(exp(post_int$I[,3,3] - post_int$I[,1,3])) # Intervention, Level
mean(exp(post_int$I[,4,3] - post_int$I[,1,3])) # Intervention, Level
```


```{r}
mean(exp(post_int$I[,2,2] - post_int$I[,1,2])) # Intervention, Level
mean(exp(post_int$I[,3,2] - post_int$I[,1,2])) # Intervention, Level
mean(exp(post_int$I[,4,2] - post_int$I[,1,2])) # Intervention, Level
```


```{r}
mean(exp(post_int$I[,2,1] - post_int$I[,1,1])) # Intervention, Level
mean(exp(post_int$I[,3,1] - post_int$I[,1,1])) # Intervention, Level
mean(exp(post_int$I[,4,1] - post_int$I[,1,1])) # Intervention, Level
```





```{r}
df %>% group_by(position, intervention) %>% count(gender)
```

